---
title: "Gapminder"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
```

## Introduction

In this document we will be exploring the Gapminder dataset.

## Observations of Gapminder

### Countries with life expectancy less than 30

```{r}
gapminder %>% filter(lifeExp<30)
```
**Two** observations in the dataset had a life expectancy from birth of less than 30.  This includes Afghanistan in 1952 and Rwanda in 1992.

### Countries with life expectancy greater than 81

```{r}
gapminder %>% filter(lifeExp>81)
```
**Seven** observations in the Gapminder dataset have had a life expectancy from birth of more than 81 years.  This included Australia, Iceland, Hong Kong, Japan and Switzerland in 2007 and Hong Kong and Japan in 2002.

### Life Expectancy by continent in 2007

```{r}
gapminder2<-filter(gapminder,year==2007)
boxplot(lifeExp~continent,data=gapminder2)
```
In 2007 Oceania had the highest median life expectancy, followed by Europe, Americas, Asia and lastly Africa.

